---
title: "peRspective"
output: github_document
---

```{r, setup, echo = F}
knitr::opts_chunk$set(message = F, warning = F)
```


Perspective is an API that uses machine learning models to score the perceived impact a comment might have on a conversation. [Website](http://www.perspectiveapi.com/).

`peRspective` provides access to the API using the R programming language.

For an excellent documentation of the Perspective API see [here](https://github.com/conversationai/perspectiveapi/blob/master/api_reference.md).


## Setup

### API authorization

In order to get the Perspective API working you need to create a Google Cloud project in your [Google Cloud console](https://console.developers.google.com/). You can also use an existing project, if you have one.

Once you have a project set up go to [Perspective API's overview page](https://console.developers.google.com/apis/api/commentanalyzer.googleapis.com/overview) and click **_Enable_**.

Finally, you need to obtain an API key. You can do this on the [API credentials page](https://console.developers.google.com/apis/credentials), just click **_Create credentials_**, and choose "API Key". Story your API key safely.

Now you are ready to make a request to the Perspective API!

### Quota and character length Limits

You can check your quota limits by going to [your google cloud project's Perspective API page](https://console.cloud.google.com/apis/api/commentanalyzer.googleapis.com/quotas), and check 
your projects quota usage at 
[the cloud console quota usage page](https://console.cloud.google.com/iam-admin/quotas).

The maximum text size per request is 3000 bytes.

### In R

Install package from GitHub:

```{r, eval = F}
devtools::install_github("favstats/peRspective")
```

Load package:

```{r}
library(peRspective)
```

Also the `tidyverse` for examples.

```{r}
library(tidyverse)
```

## Models

### Alpha

The following alpha models are **recommended** for use. They have been tested
across multiple domains and trained on hundreds of thousands of comments tagged
by thousands of human moderators. These are available in **English (en) and Spanish (es)**.

*   **TOXICITY**: rude, disrespectful, or unreasonable comment that is likely to
    make people leave a discussion. This model is a
    [Convolutional Neural Network](https://en.wikipedia.org/wiki/Convolutional_neural_network) (CNN)
    trained with [word-vector](https://www.tensorflow.org/tutorials/word2vec)
    inputs.
*   **SEVERE_TOXICITY**: This model uses the same deep-CNN algorithm as the
    TOXICITY model, but is trained to recognise examples that were considered
    to be 'very toxic' by crowdworkers. This makes it much less sensitive to
    comments that include positive uses of curse-words for example. A labelled dataset
    and details of the methodolgy can be found in the same [toxicity dataset](https://figshare.com/articles/Wikipedia_Talk_Labels_Toxicity/4563973) that is
    available for the toxicity model.

### Experimental

#### Experimental toxicity sub-attributes definitions

The following experimental models give more fine-grained classifications than
overall toxicity. They were trained on a relatively smaller amount of data
compared to the primary toxicity models above and have not been tested as
thoroughly.

*   **IDENTITY_ATTACK**: negative or hateful comments targeting someone because of their identity.
*   **INSULT**: insulting, inflammatory, or negative comment towards a person
    or a group of people.
*   **PROFANITY**: swear words, curse words, or other obscene or profane
    language.
*   **THREAT**: describes an intention to inflict pain, injury, or violence
    against an individual or group.
*   **SEXUALLY_EXPLICIT**: contains references to sexual acts, body parts, or
    other lewd content.
*   **FLIRTATION**: pickup lines, complimenting appearance, subtle sexual
    innuendos, etc.

For more details on how these were trained, see the [Toxicity and sub-attribute annotation guidelines](https://github.com/conversationai/conversationai.github.io/blob/master/crowdsourcing_annotation_schemes/toxicity_with_subattributes.md).


### New York Times moderation models

The following experimental models were trained on New York Times data tagged by
their moderation team.

*   **ATTACK_ON_AUTHOR**: Attack on the author of an article or post.
*   **ATTACK_ON_COMMENTER**: Attack on fellow commenter.
*   **INCOHERENT**: Difficult to understand, nonsensical.
*   **INFLAMMATORY**: Intending to provoke or inflame.
*   **LIKELY_TO_REJECT**: Overall measure of the likelihood for the comment to
    be rejected according to the NYT's moderation.
*   **OBSCENE**: Obscene or vulgar language such as cursing.
*   **SPAM**: Irrelevant and unsolicited commercial content.
*   **UNSUBSTANTIAL**: Trivial or short comments.

Here is a list of currently supported models:

```{r, echo=F}
tibble::tribble(
  ~`Model Attribute Name`,  ~Version,                                  ~`Supported Languages`,
             "TOXICITY",     "Alpha",                                  "en, es", 
      "SEVERE_TOXICITY",     "Alpha",                                  "en, es",
      "IDENTITY_ATTACK",     "Experimental toxicity sub-attribute",    "en",
               "INSULT",     "Experimental toxicity sub-attribute",    "en", 
            "PROFANITY",     "Experimental toxicity sub-attribute",    "en",
    "SEXUALLY_EXPLICIT",     "Experimental toxicity sub-attribute",    "en",
               "THREAT",     "Experimental toxicity sub-attribute",    "en", 
           "FLIRTATION",     "Experimental toxicity sub-attribute",    "en", 
     "ATTACK_ON_AUTHOR",     "NYT moderation models",                  "en",
  "ATTACK_ON_COMMENTER",    "NYT moderation models",                  "en",
           "INCOHERENT",     "NYT moderation models",                  "en",
         "INFLAMMATORY",     "NYT moderation models",                  "en",
     "LIKELY_TO_REJECT",     "NYT moderation models",                  "en",
              "OBSCENE",     "NYT moderation models",                  "en",
                 "SPAM",     "NYT moderation models",                  "en",
        "UNSUBSTANTIAL",     "NYT moderation models",                  "en"
  ) %>% 
  knitr::kable()

```

A character vector that includes all supported models can be obtained like this:

```{r}
peRspective::prsp_models
```

## Usage

First, define your key variable:

```{r, echo = F}
key <- readr::read_lines("../keys/prsp.txt")

Sys.setenv(perspective_api_key = key)

# perspective_api_key()
```

`peRspective` functions will read the API key from environment variable `perspective_api_key`. You can assign an environment object like this in your script:


```{r, eval = F}
Sys.setenv(perspective_api_key = "YOUR_API_KEY")
```

Next, you can use `prsp_score` function to your comments scored with various models provided by the Perspective API.

```{r, eval = T}

my_text <- "Hello whats going on? Please don't leave. I need to be free."

text_scores <- prsp_score(
           text = my_text, 
           languages = "en",
           score_model = peRspective::prsp_models
           )

text_scores %>% 
  gather() %>% 
  mutate(key = fct_reorder(key, value)) %>% 
  ggplot(aes(key, value)) +
  geom_col() +
  coord_flip()
```

A Trump Tweet

```{r}
trump_tweet <- "The Fake News Media has NEVER been more Dishonest or Corrupt than it is right now. There has never been a time like this in American History. Very exciting but also, very sad! Fake News is the absolute Enemy of the People and our Country itself!"

text_scores <- prsp_score(
           trump_tweet, 
           score_sentences = F,
           score_model = peRspective::prsp_models
           )

text_scores %>% 
  gather() %>% 
  mutate(key = fct_reorder(key, value)) %>% 
  ggplot(aes(key, value)) +
  geom_col() +
  coord_flip()
```


Let's try something else:

```{r, eval = T, fig.width=12, fig.height=8}
trump_tweet <- "The Fake News Media has NEVER been more Dishonest or Corrupt than it is right now. There has never been a time like this in American History. Very exciting but also, very sad! Fake News is the absolute Enemy of the People and our Country itself!"

text_scores <- prsp_score(
           trump_tweet, 
           score_sentences = T,
           score_model = peRspective::prsp_models
           )

text_scores %>% 
  unnest(sentence_scores) %>% 
  select(type, score, sentences) %>% 
  gather(value, key, -sentences, -score) %>% 
  mutate(key = fct_reorder(key, score)) %>% 
  ggplot(aes(key, score)) +
  geom_col() +
  coord_flip() +
  facet_wrap(~sentences, ncol = 2) +
  theme_minimal() +
  geom_hline(yintercept = 0.5, linetype = "dashed")


```

```{r}
spanish_text <- "Con la llegado de internet y de las nuevas tecnologías de la información, la forma de contactar que tenemos entre los seres humanos ha cambiado y lo va a seguir haciendo en un futuro no muy lejano."


text_scores <- prsp_score(
           text = spanish_text, 
           languages = "es",
           key = key,
           score_model = c("TOXICITY", "SEVERE_TOXICITY")
           )

text_scores %>% 
  gather() %>% 
  mutate(key = fct_reorder(key, value)) %>% 
  ggplot(aes(key, value)) +
  geom_col() +
  coord_flip()
```
